### 2014-06-28 alex/albania.Rmd
getting ready to put onto template

df$group = paste0(df$CNT, df$variable)
qplot(x = numposs, y = value, data = df, facets = ~OECD, geom = "line", color = variable, group = group) + ylab("test scores") + xlab("number of possessions")

@@

```{r OUTHOURS, echo=FALSE, fig.width=15, warning=FALSE, message=FALSE}
ggplot(subset(student2012.sub, !is.na(OUTHOURS)), aes(x = OUTHOURS, fill = CNT)) + geom_density(alpha = I(0.4)) + facet_wrap(~OECD) + theme(legend.position = "none")
qplot(x = OUTHOURS, data = student2012.sub, geom = "density", facets = ~CNT, fill = I("grey"))
qplot(x = OUTHOURS, data = student2012.sub %>% filter(CNT == "Albania"), geom="density", fill = I("grey"))
qplot(x = OUTHOURS, data = student2012.sub %>% filter(CNT == "Albania"))
```

@@

qplot(x = ST15Q01, y = value, color = variable, facets = ~OECD, data = father.df, group = group, geom = "line") + xlab("father's employment status") + ylab("test scores")
```

@@

qplot(x = SC22Q01, y = value, color = variable, facets = ~OECD, data = truancy.df, group = group, geom = "line") + xlab("reported truancy") + ylab("test scores")
```

```{r gendergap, echo=FALSE, warning = FALSE}
scores = student2012 %>%
  select(CNT, math, read, ST04Q01, OECD) %>% 
  group_by(OECD, CNT, ST04Q01) %>%
  summarise(math = mean(math), read = mean(read))
male = scores %>% filter(ST04Q01 == "Male")
female = scores %>% filter(ST04Q01 == "Female")
scores.df = data.frame(OECD = male$OECD, CNT = male$CNT, math_difference = male$math - female$math, read_difference = male$read - female$read)

scores.df$CNT = factor(scores.df$CNT, levels = scores.df$CNT[order(scores.df$math_difference)])
qplot(CNT, math_difference, data = scores.df, color = OECD, size = OECD) + coord_flip() +
  scale_y_continuous("math score gap: male - female scores", breaks=seq(-30, 30, 5)) +
  geom_hline(yintercept=0, colour="grey80") + theme_bw() + scale_size_manual(values = c(4, 2.5, 2.5)) + xlab("")

scores.df$CNT = factor(scores.df$CNT, levels = scores.df$CNT[order(scores.df$read_difference)])
qplot(CNT, read_difference, data = scores.df, color = OECD, size = OECD) + coord_flip() +
  scale_y_continuous("read score gap: male - female scores") +
  geom_hline(yintercept=0, colour="grey80") + theme_bw() + scale_size_manual(values = c(4, 2.5, 2.5)) + xlab("")
```

>>>>

df$group = paste0(df$CNT, df$variable)
qplot(x = numposs, y = value, data = df, facets = ~OECD, geom = "line", color = variable, group = group) + ylab("test scores") + xlab("number of possessions") + scale_colour_discrete(name = "Subject", labels=c("Math", "Science", "Reading"))

@@

```{r OUTHOURS, echo=FALSE, fig.width=15, warning=FALSE, message=FALSE}
ggplot(subset(student2012.sub, !is.na(OUTHOURS)), aes(x = OUTHOURS, fill = CNT)) + geom_density(alpha = I(0.4)) + facet_wrap(~OECD) + theme(legend.position = "none") + scale_x_continuous("out of school study time (hours)", limits = c(0, 65))

qplot(x = OUTHOURS, data = student2012.sub, geom = "density", facets = ~CNT, fill = I("grey")) 
qplot(x = OUTHOURS, data = student2012.sub %>% filter(CNT == "Albania"), geom="density", fill = I("grey"))
qplot(x = OUTHOURS, data = student2012.sub %>% filter(CNT == "Albania"))
```

@@

qplot(x = ST15Q01, y = value, color = variable, facets = ~OECD, data = father.df, group = group, geom = "line") + xlab("father's employment status") + ylab("test scores") + scale_colour_discrete(name = "Subject", labels=c("Math", "Science", "Reading"))
```

@@

qplot(x = SC22Q01, y = value, color = variable, facets = ~OECD, data = truancy.df, group = group, geom = "line") + xlab("reported truancy") + ylab("test scores") + scale_colour_discrete(name = "Subject", labels=c("Math", "Science", "Reading"))
```

```{r gendergap, echo=FALSE, warning = FALSE, fig.height = 10}
scores = student2012 %>%
  select(CNT, math, read, ST04Q01, OECD) %>% 
  group_by(OECD, CNT, ST04Q01) %>%
  summarise(math = mean(math), read = mean(read))
male = scores %>% filter(ST04Q01 == "Male")
female = scores %>% filter(ST04Q01 == "Female")
scores.df = data.frame(OECD = male$OECD, CNT = male$CNT, math_difference = male$math - female$math, read_difference = male$read - female$read)

scores.df$CNT = factor(scores.df$CNT, levels = scores.df$CNT[order(scores.df$math_difference)])
qplot(CNT, math_difference, data = scores.df, color = OECD, size = OECD) + coord_flip() +
  scale_y_continuous("math score gap: male - female scores", breaks=seq(-30, 30, 5)) +
  geom_hline(yintercept=0, colour="grey80") + scale_size_manual(values = c(4, 2.5, 2.5)) + xlab("")

scores.df$CNT = factor(scores.df$CNT, levels = scores.df$CNT[order(scores.df$read_difference)])
qplot(CNT, read_difference, data = scores.df, color = OECD, size = OECD) + coord_flip() +
  scale_y_continuous("read score gap: male - female scores") +
  geom_hline(yintercept=0, colour="grey80") + scale_size_manual(values = c(4, 2.5, 2.5)) + xlab("")

#qplot(CNT, value, data = melt(scores.df, id = c("OECD", "CNT")), color = OECD, size = OECD, facets = ~variable) + 
#  coord_flip() + xlab("") + ylab("Score difference: male - female") + scale_size_manual(values = c(4, 2.5, 2.5))
```
